% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

% \documentclass{acm_proc_article-sp}
\documentclass[10pt]{IEEEtran}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{color}
\usepackage{url}
\usepackage{citesort}
\usepackage{syntax}
\usepackage{wrapfig}
\usepackage{fancyvrb}


\def\todo#1{\textcolor{red}{\textbf{[TODO:~#1]}}\footnote{TODO:~#1}}

\begin{document}


\title{CloudFlow: Cloud-wide policy enforcement using fast VM introspection}


\author{
    \IEEEauthorblockN{Mirza Basim Baig, Connor Fitzsimons, Suryanarayanan Balasubramanian,\\ Radu Sion and Donald Porter\\ }
    \IEEEauthorblockA{Computer Science, Stony Brook University \\
    \{mbaig,crfitzsimons,sbalasubrama,sion,porter\}@cs.stonybrook.edu}
}


% \author{
% \alignauthor
%   Mirza Basim Baig, Connor Fitzsimons, Suryanarayanan Balasubramanian,\\ Radu Sion and Don Porter\\
%       \affaddr{Computer Science, Stony Brook University}\\
%       \email{\{mbaig,crfitzsimons,sbalasubrama,sion,porter\}@cs.stonybrook.edu}  
% }

\maketitle

\begin{abstract}

Increasingly government and commercial enterprises are considering cloud adoption. 
%
Clouds share hardware resources across a number of software virtual
machines.  While this carries the promise of increasingly efficient hardware 
utilization, it also comes with inherent side-channel vulnerabilities which
can be used to mount attacks that cause undesired information leakage.

This is especially important in infrastructures shared by multiple
regulatory constrained, security-disjoint principals. A classic example is a
financial company with multiple departments under the incidence of Chinese Wall 
style regulatory policies designed to curtail illicit gains and conflicts.

And, while at the individual node level, the prevention of side channels is
hard without sacrificing efficiency, a unique mitigation opportunity exists
cloud-wide.  By reactively enforcing information flow invariants through
run-time introspection and on-demand virtual machine migration we can prevent undesired
node-level side-channels with minimal performance overhead.

In this paper we introduce CloudFlow -- an information flow control
mechanism for OpenStack that deploys a new, fast virtual machine introspection mechanism
(orders of magnitude faster than previous approaches) to efficiently and
transparently enable policy enforcement cloud-wide.

CloudFlow mitigates undesirable side-channels, provides protection against undesirable
information leaks and forms a powerful tool enabling information flow policy 
enforcement at cloud scope. Additionally, CloudFlow has potential uses for cloud management and resource-efficient virtual machine scheduling.

\end{abstract}
%\vspace{-5pt}
% A category with the (minimum) three required fields
%\category{D.4.6}{Operating System}{Security and Protection}
%\vspace{-5pt}
%\terms{Security}
%\vspace{-5pt}
%\keywords{Cloud computing, Policy enforcement, VM Introspection, Information flow control} % NOT required for Proceedings

%introduction
\input{introduction.tex}

%Background and threat model
\input{model.tex}

%Architecture/Implementation
\input{architecture.tex}

%Discussion
\input{discussion.tex}

%Evaluation
\input{evaluation.tex}

%Conclusion and Future Work
\input{conclusion.tex}

\bibliographystyle{plain}
\bibliography{bib/refs}

%\input{appendix.tex}


\end{document}
